---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sanba v0.0.2

<!-- badges: start -->
[![R-CMD-check](https://github.com/Fradenti/sanba/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Fradenti/sanba/actions/workflows/R-CMD-check.yaml)
[![Last Commit](https://img.shields.io/github/last-commit/fradenti/sanba)](https://github.com/fradenti/sanba)
[![CRAN](https://www.r-pkg.org/badges/version/sanba)](https://cran.r-project.org/package=sanba)
[![Downloads (monthly)](https://cranlogs.r-pkg.org/badges/sanba?color=brightgreen)](https://www.r-pkg.org/pkg/sanba)
[![Downloads (total)](https://cranlogs.r-pkg.org/badges/grand-total/sanba?color=brightgreen)](https://www.r-pkg.org/pkg/sanba)
<!-- badges: end -->


The goal of `sanba` is to estimate Bayesian nested mixture models via MCMC and VI methods. Specifically, the package implements the common atoms model (Denti et al., 2023) and hybrid finite-infinite models (D'Angelo and Denti, 2024). All models use Gaussian mixtures with a normal-inverse-gamma prior distribution on the parameters. Additional functions are provided to help analyzing the results of the fitting procedure.    

## Installation

You can install the development version of `sanba` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Fradenti/sanba")
```



## Examples 

### Fitting via MCMC


```{r example1}
library(sanba)
set.seed(123)
y <- c(rnorm(160), rnorm(40, 5))
g <- rep(1:2, rep(100, 2))
plot(density(y[g==1]), xlim = c(-5,10), main = "Group-specific density")
lines(density(y[g==2]), col = 2)

out_mcmc <- fit_CAM(y = y, group = g, est_method = "MCMC", mcmc_param = list(nrep = 5000, burn=3000))
out_mcmc
plot(out_mcmc)
```

### Fitting via VI

```{r example2}
library(sanba)
set.seed(123)
y <- c(rnorm(160), rnorm(40, 5))
g <- rep(1:2, rep(100, 2))
plot(density(y[g==1]), xlim = c(-5,10), main = "Group-specific density")
lines(density(y[g==2]), col = 2)

out_vi <- fit_fiSAN(y, group = g, est_method = "VI", vi_param = list(n_runs = 100))
out_vi
plot(out_vi)
```

# References

D’Angelo, L., and Denti, F. (2024). A Finite-Infinite Shared Atoms Nested Model for the Bayesian Analysis of Large Grouped Data Sets. *Bayesian Analysis* \doi{10.1214/24-BA1458}

Denti, F., Camerlenghi, F., Guindani, M., Mira, A., 2023. A Common Atoms Model for the Bayesian Nonparametric Analysis of Nested Data. *Journal of the American Statistical Association*. 118(541), 405–416. \doi{10.1080/01621459.2021.1933499}

