---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SANba v0.1.0

<!-- badges: start -->
[![R-CMD-check](https://github.com/fradenti/SANba/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/fradenti/SANba/actions/workflows/R-CMD-check.yaml)
[![Last Commit](https://img.shields.io/github/last-commit/fradenti/SANvi)](https://github.com/fradenti/SANvi)
<!-- badges: end -->

SANba is a meta-package for the Bayesian analysis of grouped data using shared atoms nested models. It encompasses both `SANple` and `SANvi`. The former package can be used to estimate nested models with MCMC, the second implements variational inference methods.

## Installation

You can install the development version of SANba like so:

```{r,eval=F} 
remotes::install_github("fradent/SANba")
```

## Load both `SANple` and `SANvi`

```{r example}
library(SANba)
```

For more information, see 

* the [SANple repo](https://github.com/laura-dangelo/SANple)
* the [SANple package](https://cran.r-project.org/web/packages/SANple/index.html)  
* the [SANvi repo](https://github.com/fradenti/SANvi)  
* the [SANvi package](https://cran.r-project.org/web/packages/SANvi/index.html)
